An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-31 VLDB2026/main.tex

\textit{\textbf{Index size.}}
\textcolor{orange}{
	As shown in Figure~\ref{fig:index_size_mb_comparison_query1}, PASE exhibits significantly larger index sizes across all supported datasets, mainly due to its reliance on a large amount of metadata. For regular-scale datasets, other methods show moderate variation. However, on large-scale dataset, Graph-based algorithms such as ACORN, FilteredDiskANN, and UNG tend to exhibit a sharp increase in index size, primarily due to the large number of candidate neighbors they maintain. Overall, IVF-based methods tend to produce more compact indexes.
}

@@

	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}} 
	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:range-cross-platform}. Although the third-ranked algorithm differs, we consider the ranking order essentially unchanged since the performance of the third and fourth algorithms is comparable. So our findings remain consistent with those reported in Section 4.2.4. For brevity and due to space limitations, we omit further discussion of these redundant results.}
%	\textcolor{cyan}{Consistent with Section 4.2.4, we conducted additional range filtering experiments using the YT-Audio-Real dataset on the same server, with results shown in Figure \ref{fig:Different Computer range}. Compared with the original server's experimental results (Figure \ref{fig:exp_8_2}($e$)), the conclusions remain identical to those described in Section 4.2.4. Due to space constraints, these details are not reiterated here.}

	\textit{\textbf{\textcolor{red}{Large-scale Datasets.}}} \textcolor{red}{As shown in the figure~\ref{fig: range big dataset}, On the 100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged. However, their high performance is achieved at the cost of extremely high memory consumption, as detailed in Figure~\ref{fig:rangeFilter_search_memory_mb}. Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top three algorithms}.

>>>>

\textit{\textbf{Index size.}}
\textcolor{orange}{
	As shown in Figure~\ref{fig:index_size_mb_comparison_query1}, PASE exhibits significantly larger index sizes across all supported datasets, mainly due to its reliance on a large amount of metadata. For medium-scale datasets, other methods show moderate variation. However, on large-scale dataset, Graph-based algorithms such as ACORN, FilteredDiskANN, and UNG tend to exhibit a sharp increase in index size, primarily due to the large number of candidate neighbors they maintain. Overall, IVF-based methods tend to produce more compact indexes.
}

@@

	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}} 
	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:range-cross-platform}. Although the third-ranked algorithm differs, we consider the ranking order remains stable since the performance of the third and fourth algorithms is comparable. So our findings remain consistent with those reported in Section 4.2.4. For brevity and due to space limitations, we omit further discussion of these redundant results.}
%	\textcolor{cyan}{Consistent with Section 4.2.4, we conducted additional range filtering experiments using the YT-Audio-Real dataset on the same server, with results shown in Figure \ref{fig:Different Computer range}. Compared with the original server's experimental results (Figure \ref{fig:exp_8_2}($e$)), the conclusions remain identical to those described in Section 4.2.4. Due to space constraints, these details are not reiterated here.}

	\textit{\textbf{\textcolor{red}{Large-scale Datasets.}}} \textcolor{red}{As shown in the figure~\ref{fig: range big dataset}, On the deep100M dataset, the top 3 ranked algorithms (WinFilter, UNIFY, and iRange) remain unchanged. However, their high performance is achieved at the cost of extremely high memory consumption, as detailed in Figure~\ref{fig:rangeFilter_search_memory_mb}. Meanwhile, VBASE and Faiss demonstrate moderate performance but significantly lower memory consumption than the top three algorithms}.
